Untitled

### 2022-11-16 Manuscript/Ms.Rmd
reorganising files
edits

---
title: "Bee brain size is positively associated with urban lifestyles but not with positive population trends"
output: pdf_document

@@

header-includes:
- \usepackage{orcidlink}
- \usepackage{caption,setspace}
- \captionsetup[figure]{labelformat=empty}

---

@@

@@

```{r, echo=FALSE, message=FALSE, cache=FALSE, warning=FALSE, fig.align="center", fig.height=12, fig.width=12, fig.cap="\\textbf{Figure 1.} Maps showing the location of the downloaded GBIF occurrences for the different bee species."}

@@

@@

#Phylogenetic tree for USA and Europe
library(ggtree) 
library(ggplot2)
library(stringr)
library(tidyverse)
library(tibble)

@@

#Plot tree
p <- ggtree(bee.tree100) %<+% brain_weight  +  aes(color=Country) +  geom_tree(size=0.8)+
    geom_tippoint(aes(size = residuals, color=Country))+ 
    theme_tree2()+scale_size_continuous(range = c(-1.2, 3.2),name="Residuals")+
    scale_color_manual(name = "Data", values=c("darkgoldenrod1","cyan4","black"),
                       labels = c("Europe", "USA", "USA and Europe"),
                       breaks = c("Europe", "USA", "USA and Europe")) +
  ggtitle("A") + theme(plot.title = element_text(size=18, face="bold"))

#Convert wide format to long for plotting heatmap
d=gather(preferences, condition, measurement, Agricultural:Seminatural, factor_key=TRUE)

#Relevel for plotting
d = d %>% 
mutate(condition = recode_factor(condition, "Seminatural" = "Semideveloped")) %>% 
mutate(condition=fct_relevel(condition,c("Natural","Agricultural","Semideveloped", "Urban")))

p2 = ggplot(d, aes(x=condition, y=Species)) + 
    geom_tile(aes(fill=measurement),color = "white") +
   # scale_fill_gradient(high="black",  low="white") +
       scale_fill_viridis_c(name = "Habitat\n preference", limits=c(0, 1), breaks=c(0.1, 0.5, 0.9), labels=c("Low","","High")) + 
    theme_minimal() +
    xlab(NULL) + 
    ylab(NULL) + 
    theme(axis.text.x = element_text(face="bold", color="black", 
    size=10,  vjust=1.15),
    axis.text.y = element_text(face="italic", color="black", size=7, hjust=0),
    plot.title = element_text(size=18, face="bold")) +
  ggtitle("B")

@@

```{r, echo=FALSE, message=FALSE, cache=FALSE, warning=FALSE,fig.align="center", fig.height=6, fig.width=10, fig.cap="\\textbf{Figure 3.} Frequency distribution of the bee preferences for each habitat type (i.e., natural, agricultural, semideveloped and urban). The different habitats are reclassifications from the 2006 land use categories of the Corine Land Cover (CLC) inventory for Europe and the National Land Cover (NLC) database for Unites States."}

#Histogram of habitat preferences
#Load libraries
library(tidyverse)

@@

#Convert to long to model everything at the same time
long_data = preferences %>% gather(Habitat, Preference, 2:5, -c(Species))

#Relevel for plotting
long_data = long_data %>% 
    mutate(Habitat = recode_factor(Habitat, "Seminatural" = "Semideveloped")) %>% 
    mutate(Habitat=fct_relevel(Habitat,c("Natural","Agricultural","Semideveloped", "Urban")))

@@

#Plot
ggplot(long_data, aes(x=Preference, color= Habitat)) +
    geom_histogram(aes(fill= Habitat)) + 
    xlab("Habitat preference") +
    ylab("Frequency") +
    facet_wrap(~ Habitat) +
    scale_colour_viridis_d(end=0.98)+
    scale_fill_viridis_d(end=0.98) +
    theme_bw()+
    theme(axis.title = element_text(face = "bold", size=14), 
    strip.text.x = element_blank() , strip.background = element_blank(),
    panel.border=element_rect(size=0.8))+
    scale_x_continuous(breaks = seq(from = 0, to = 1, by = 0.5),
                       labels = paste0(c(0,0.5,1), "\n", labels.minor)) +
    scale_y_continuous(expand = c(0, 0))+
    geom_vline(aes(xintercept = 0.05), colour="black", linetype="dashed") +
    geom_vline(aes(xintercept = 0.95), colour="black", linetype="dashed")

@@

@@

>>>>

---
title: "Bee brain size is positively associated with urban lifestyles but not with positive population trends"
output:
  pdf_document:
    fig_caption: yes

@@

header-includes:
- \usepackage{orcidlink}
- \usepackage{caption,setspace}
- \captionsetup[figure]{labelformat=empty}
- \usepackage{float} 
- \floatplacement{figure}{H} 
---

```{r echo=FALSE,warning=FALSE}

knitr::opts_chunk$set(fig.pos = "H", out.extra = "")
```

@@

Relevant refs:

https://onlinelibrary.wiley.com/doi/10.1111/ele.14133?af=R

@@

\clearpage

```{r, echo=FALSE, message=FALSE, cache=FALSE, warning=FALSE, fig.align="center", fig.height=12, fig.width=12, fig.cap="\\textbf{Figure 1.} Maps showing the study areas and the number of GBIF occurrences in logarithmic scale for the selected bee species (N = 85). A) European continent with records downloaded for England, Belgium, Netherlands, Germany and Denmark. B) East Coast of Unites States with records for Vermont, New Hampshire, Massachusetts, Rhode Island, Connecticut, New York metropolitan area, New Jersey, Delaware and Maryland.", fig.pos="p"}

@@

\clearpage

@@

library(ggtree) #v3.5.3.002
library(ggplot2)
library(stringr)
library(tidyverse)
library(tibble)

@@

#Plot tree
p <- ggtree(bee.tree100) %<+% brain_weight  +  aes(color=Country)+
    geom_tippoint(aes(size = residuals, color=Country))+
    theme_tree2()+scale_size_continuous(range = c(-1, 3.6),name="Residuals")+
    scale_color_manual(name = "Data", values=c("darkgoldenrod1","cyan4","black"),
                       labels = c("Europe", "USA", "USA and Europe"),
                       breaks = c("Europe", "USA", "USA and Europe")) +
  ggtitle("A") + theme(plot.title = element_text(size=18, face="bold"))

#Convert wide format to long for plotting heatmap
d=gather(preferences, condition, measurement, Agricultural:Urban, factor_key=TRUE)

#Relevel for plotting
d = d %>% 
mutate(condition=fct_relevel(condition,c("Natural","Agricultural", "Urban")))

p2 = ggplot(d, aes(x=condition, y=Species)) + 
    geom_tile(aes(fill=measurement),color = "white") +
   # scale_fill_gradient(high="black",  low="white") +
    scale_fill_viridis_c(name = "Habitat\n preference") + 
    theme_minimal() +
    xlab(NULL) + 
    ylab(NULL) + 
    theme(axis.text.x = element_text(face="bold", color="black", 
    size=7.5,  vjust=1.15),
    axis.text.y = element_text(face="italic", color="black", size=7.5, hjust=0),
    plot.title = element_text(size=18, face="bold")) +
   ggtitle("B")

@@

```{r, echo=FALSE, message=FALSE, cache=FALSE, warning=FALSE,fig.align="center", fig.height=4, fig.width=10, fig.cap="\\textbf{Figure 3.} Frequency distribution of the bee preferences for each habitat type (i.e., natural, agricultural and urban). The different habitats are reclassifications from the 2006 land use categories of the Corine Land Cover (CLC) inventory for Europe and the National Land Cover (NLC) database for Unites States.", fig.pos="p"}

@@

#Convert to long to model everything at the same time
long_data = preferences %>% gather(Habitat, Preference, 2:4, -c(Species))

#Relevel for plotting
long_data = long_data %>% 
    mutate(Habitat=fct_relevel(Habitat,c("Natural","Agricultural", "Urban")))

@@

long_data$Habitat <- factor(long_data$Habitat, levels = c("Natural", "Agricultural", "Urban"),
                  labels = c("A) Natural", "B) Agricultural", "C) Urban"))

#Plot
ggplot(long_data, aes(x=Preference, color= Habitat)) +
    geom_histogram(aes(fill= Habitat)) + 
    xlab("Habitat preference") +
    ylab("Frequency") +
    facet_wrap(~ Habitat) +
    scale_colour_viridis_d(end=0.98)+
    scale_fill_viridis_d(end=0.98) +
    theme_bw() +   
    theme(axis.title = element_text(face = "bold"),
    panel.border=element_rect(size=1), 
    legend.position = "none",
    strip.text = element_text(face = "bold", size = 18,hjust = -0.01),
    strip.background = element_rect(fill = NA, colour = NA, size = 0,linetype="solid"))+
    scale_x_continuous(breaks = seq(from = 0, to = 1, by = 0.5),
                       labels = paste0(c(0,0.5,1), "\n", labels.minor)) +
    scale_y_continuous(expand = c(0, 0), limits = c(0,60))+
    geom_vline(aes(xintercept = 0.05), colour="black", linetype="dashed") +
    geom_vline(aes(xintercept = 0.95), colour="black", linetype="dashed")

@@

\clearpage

```{r, echo=FALSE, message=FALSE, cache=FALSE, warning=FALSE,fig.align="center", fig.height=6, fig.width=10, fig.cap="\\textbf{Figure 4.}", fig.pos="p"}

#Load libraries
library(readr)
library(dplyr)
library(ggplot2)

#Load data for plotting
long_data <- read_csv("../Data/Europe_USA/data_preference_residuals_europe_usa_qualitative.csv")

model1 = read_csv("../Data/Europe_USA/model_output_preference_residuals_europe_usa_qualitative.csv")

model2 = read_csv("../Data/Europe_USA/model_output_preference_brain_weight_europe_usa_qualitative.csv")

model3 = read_csv("../Data/Europe_USA/model_output_preference_it_europe_usa_qualitative.csv")

#Relevel for plotting
long_data = long_data %>% 
    mutate(Habitat=fct_relevel(Habitat,c("Natural","Agricultural", "Urban"))) 
#Relevel for plotting
model1 = model1 %>% 
    mutate(Habitat=fct_relevel(Habitat,c("Natural","Agricultural", "Urban"))) 
#Relevel for plotting
model2 = model2 %>% 
    mutate(Habitat=fct_relevel(Habitat,c("Natural","Agricultural", "Urban"))) 
#Relevel for plotting
model3 = model3 %>% 
    mutate(Habitat=fct_relevel(Habitat,c("Natural","Agricultural", "Urban")))

#colorBlindness::displayAllColors(viridis::viridis(4))

all_1 = ggplot(model1, aes(x = residuals, y = estimate__, color=Habitat)) +
geom_point(data =  long_data, aes(x = residuals, y = (Preference)), shape=21, size=2.5) +
geom_line(aes(color=Habitat),size=0.7) +
geom_ribbon(aes(ymin = lower__, ymax = upper__,  fill = Habitat),color=NA, linetype = "dashed",alpha = 0.2)+
theme_bw() +
ylab("Habitat preference") +
xlab("Residuals") +
scale_colour_viridis_d() +
scale_fill_viridis_d() +
scale_y_continuous(breaks = seq(0, 1, by = 1),labels = c("Low", "High")) +
ggtitle("A") +
theme(plot.title = element_text(face = "bold", size=18))

all_2 = ggplot(model2, aes(x = Brain.weight, y = estimate__, color=Habitat)) +
geom_point(data =  long_data, aes(x = Brain.weight, y = (Preference)), shape=21, size=2.5) +
geom_line(aes(color=Habitat),size=0.7) +
geom_ribbon(aes(ymin = lower__, ymax = upper__,  fill = Habitat),color=NA, linetype = "dashed",alpha = 0.2)+
theme_bw() +
ylab(NULL) +
xlab("Brain weight (mg)") +
scale_colour_viridis_d() +
scale_fill_viridis_d() +
scale_y_continuous(breaks = seq(0, 1, by = 1),labels = c("Low", "High")) +
ggtitle("B") +
theme(plot.title = element_text(face = "bold", size=18))

all_3 = ggplot(model3, aes(x = IT, y = estimate__, color=Habitat)) +
geom_point(data =  long_data, aes(x = IT, y = (Preference)), shape=21, size=2.5) +
geom_line(aes(color=Habitat),size=0.7) +
geom_ribbon(aes(ymin = lower__, ymax = upper__, fill = Habitat),color=NA, linetype = "dashed",alpha = 0.2)+
theme_bw() +
ylab(NULL) +
xlab("Intertegular distance (mm)") +
scale_colour_viridis_d() +
scale_fill_viridis_d() +
scale_y_continuous(breaks = seq(0, 1, by = 1),labels = c("Low", "High")) +
ggtitle("C") +
theme(plot.title = element_text(face = "bold", size=18))

library(patchwork)

all_1 + (all_2/all_3) + plot_layout(guides = "collect") &
theme(legend.position = 'bottom', panel.border=element_rect(size=1),
      axis.title=element_text(face="bold"),
      legend.box.background = element_rect(colour = "black",size=1))

\clearpage

@@

\newpage

### 2022-11-16 Scripts/Figure_1_Map_Points/Map.Rmd
edits

p2 = ggplot(Europe) +
geom_sf(fill="gray70",color = "black", alpha = 1,size=0.2)+
geom_bin2d(data = all_long_lat, aes(x = long, y = lat, fill=log(..count..)),size = 1,bins=70) +
viridis::scale_fill_viridis(name = "log(Count)", breaks = c(0, 4, 8)) +
coord_sf(xlim = c(-8, 18), ylim = c(40, 60)) +
theme(panel.background = element_rect(fill = "aliceblue"),
panel.border = element_rect(colour = "black", fill=NA, size=1)) +
ylab("Latitude") +
xlab("Longitude") +
ggtitle("A") +
theme(legend.position = c(0, 1),legend.justification = c(0, 1),
legend.background = element_blank(),
legend.box.background = element_blank(),
legend.key = element_blank(), 
legend.title = element_text(face = "bold"),
axis.title = element_text(face="bold", size = 12),
plot.title = element_text(face="bold"),
legend.text = element_text(face = "bold", size = 12), legend.direction="horizontal") +
scale_y_continuous(breaks = seq(40, 60, by = 6)) +
scale_x_continuous(breaks = seq(-8, 18, by = 8)) +
guides(fill = guide_colourbar(title.position = "top", title.hjust = .5))

@@

p2 = ggplot(canada) + 
geom_sf(fill="gray70",color = "black", alpha = 1,size=0.2) + 
geom_sf(data= usa, fill="gray70",color = "black", alpha = 1,size=0.2) +
geom_bin2d(data = all_long_lat, aes(x = long, y = lat, fill=log(..count..)),size = 1,bins=50) +
viridis::scale_fill_viridis(name = "log(Count)", breaks = c(0, 3, 6)) +
coord_sf(xlim = c(-82, -68), ylim = c(33, 47))  +
theme(panel.background = element_rect(fill = "aliceblue"),
panel.border = element_rect(colour = "black", fill=NA, size=1)) +
ylab("Latitude") +
xlab("Longitude") +
ggtitle("B") +
theme(legend.position = c(0, 1),legend.justification = c(0, 1),
legend.background = element_blank(),
legend.box.background = element_blank(),
legend.key = element_blank(),
legend.title = element_text(face = "bold"),
axis.title = element_text(face="bold", size = 12),
plot.title = element_text(face="bold"),
legend.text = element_text(face = "bold", size = 12, hjust=0), legend.direction="horizontal") +
scale_y_continuous(breaks = seq(33, 47, by = 4)) +
scale_x_continuous(breaks = seq(-82, -68, by = 4)) +
guides(fill = guide_colourbar(title.position = "top", title.hjust = .5))

#Insert general plot within specific plot
panel2 = p2 + inset_element(p1, left = 0, bottom = -0.885, right = 0.35, top = 1.2, ignore_tag = TRUE)

>>>>

p2 = ggplot(Europe) +
geom_sf(fill="gray80",color = "black", alpha = 1,size=0.2)+
geom_bin2d(data = all_long_lat, aes(x = long, y = lat, fill=log(..count..)),size = 1,bins=70) +
viridis::scale_fill_viridis(name = "log(Count)", breaks = c(0, 4, 8),limits=c(0,8)) +
coord_sf(xlim = c(-8, 18), ylim = c(40, 60)) +
theme(panel.background = element_rect(fill = "white"),
panel.border = element_rect(colour = "black", fill=NA, size=1)) +
ylab("Latitude") +
xlab("Longitude") +
ggtitle("A") +
theme(legend.position = c(0, 1),legend.justification = c(0, 1),
legend.background = element_blank(),
legend.box.background = element_blank(),
legend.key = element_blank(), 
legend.title = element_text(face = "bold"),
axis.title = element_text(face="bold", size = 12),
plot.title = element_text(face="bold"),
legend.text = element_text(face = "bold", size = 12), legend.direction="horizontal") +
scale_y_continuous(breaks = seq(40, 60, by = 6)) +
scale_x_continuous(breaks = seq(-8, 18, by = 8)) +
guides(fill = guide_colourbar(title.position = "top", title.hjust = .5))

@@

p2 = ggplot(canada) + 
geom_sf(fill="gray80",color = "black", alpha = 1,size=0.2) + 
geom_sf(data= usa, fill="gray80",color = "black", alpha = 1,size=0.2) +
geom_bin2d(data = all_long_lat, aes(x = long, y = lat, fill=log(..count..)),size = 1,bins=50) +
viridis::scale_fill_viridis(name = "log(Count)", breaks = c(0, 4, 8), limits=c(0,8)) +
coord_sf(xlim = c(-82, -67), ylim = c(33, 47))  +
theme(panel.background = element_rect(fill = "white"),
panel.border = element_rect(colour = "black", fill=NA, size=1)) +
ylab("Latitude") +
xlab("Longitude") +
ggtitle("B") +
theme(legend.position = c(0, 1),legend.justification = c(0, 1),
legend.background = element_blank(),
legend.box.background = element_blank(),
legend.key = element_blank(),
legend.title = element_text(face = "bold"),
axis.title = element_text(face="bold", size = 12),
plot.title = element_text(face="bold"),
legend.text = element_text(face = "bold", size = 12, hjust=0), legend.direction="horizontal") +
scale_y_continuous(breaks = seq(33, 47, by = 4)) +
scale_x_continuous(breaks = seq(-82, -68, by = 4)) +
guides(fill = guide_colourbar(title.position = "top", title.hjust = .5))

#Insert general plot within specific plot
panel2 = p2 + inset_element(p1, left = 0, bottom = -0.86, right = 0.35, top = 1.2, ignore_tag = TRUE)
